An optimization of bidirectional update language based on the idea of reversible computing \thanks{Supported by organization x.}

### 2019-08-23 paper/main.tex

@@

\begin{itemize}
\item $s_1$ in composition is redundant.  
\item Next, we will extend this to avoid this redundant computation.
\end{itemize}

@@

\section{xpg}

\begin{itemize}
\item pg is fastest for right assoc programs and kpg is fastest for left assoc programs.
\item To combine their strength, we can use the following definition.
\item If there is a composition, we use xpg for evaluation of $bx_1$ and pg for evaluation of $bx_2$.
\item If $bx_1$ is simple program (= Right assoc), this is almost the same with pg.
\item If $bx_1$ is complicated program (= Left assoc), this is almost the same with kpg.
\end{itemize}

@@

\newpage
\section{Conclusion and Future Work}

>>>>

%\begin{itemize}
%\item Information loss causes re-evaluation of get.
%\item To prevent this, we introduced the idea of reversible computation.
%\item In reversible computation we need to keep all information: we can not lose any information.
%\item In BiGUL we can acheive this by tupling put and get.
%\item pg bx (s, v) = (put bx (s, v), get bx (s))
%\item pg: s * v $\to$ s * v
%\item No garbage
%\item This function is self-inverse. (involution, (f (f input)) = input)
%\item \textcolor{red}{Constraint: In case expression, put and get must always choose the same branch. This constraint is not satisfied in general: (e.g, SNOC, the different length of two inputs.) To remove this constraint we need to use garbage.}
%\end{itemize}

@@

\begin{itemize}
\item This is faster than pg for left assoc BX programs.
\item (Slower for right assoc programs)
\item $s_1$ in composition is redundant.  
\item Next, we will extend this to avoid this redundant computation.
\end{itemize}

@@

\subsection{xpg}

\begin{itemize}
\item So far, we focus on left assoc programs. xpg is faster than the others.
\item On the other hand, pg is fastest for right assoc programs.
\item To combine their strength, we introfuce new pg that combines pg and kpg.
\item If there is a composition, we use xpg for evaluation of $bx_1$ and pg for evaluation of $bx_2$.
\item If $bx_1$ is simple program (= Right assoc), this is almost the same with pg.
\item If $bx_1$ is complicated program (= Left assoc), this is almost the same with kpg.
\end{itemize}

@@

\section{Related Work}

\newpage

\section{Conclusion and Future Work}
